\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

My work on correctness of services started 2005 in Berlin. Three years later, I moved to Rostock. Then earlier this year, I finished my thesis in Eindhoven. Needless to say, there are \emph{many} people to thank\dots\medskip

The only person to start thanking is Karsten Wolf. In Berlin, he introduced me to the world of theoretical computer science, formal methods, and model checking. Some years later, he could offer me a job in Rostock, which really boosted my motivation to work in the area of controllability and operating guidelines. Without him, I never would have thought about an academic career. I thank him for his idea to focus on correctness in my thesis and I am looking forward to continue working with him.

Second, it is my pleasure to thank Wil van der Aalst for being a promotor of my thesis. I am grateful for his thorough feedback, his amazing enthusiasm, and his incomparable motivation. The presentation of this thesis is a result of his feedback. He was always a great guide and I thank him for the time I could spend in Eindhoven.

Third, I am grateful to Wolfgang Reisig to introduce me to Petri nets and the scientific world. He offered me a position in Berlin when I never thought about staying at university after my diploma thesis. In the years in Berlin, he made it possible for me to attend many conferences and to build a network of colleagues and friends.

I thank Mathias Weske, Marlon Dumas, Adelinde Uhrmacher, Natalia Sidorova, and Kees van Hee for their service as committee members and their valuable feedback.

Thank you Christian Stahl for always helping out, reading drafts of papers and this thesis, and taking the time to even discussing the most uncooked ideas; Gero Decker for so many fruitful discussions under Queensland's sun on choreographies and service modeling; Oliver Kopp for a constant reminder that there are people out there actually using \acronym{WS-BPEL}; Peter Massuthe for his scientific rigor; Kathrin Kaschner for giving me a warm welcome in Rostock and being such a great colleague through all these years; Christian Gierds for the many fruitful discussions on our tools and the \acronym{WS-BPEL} semantics; Dirk Fahland for the many nice years of joint research; Daniela Weinberg for her help with Wendy; and all my other colleagues. Carmen Bratosin, Arjan Mooij, Helen Schonenberg, and Marc Voorhoeve. In particular, I thank Eric Verbeek and Boudewijn van Dongen for their tremendous support and patience during integration of our \st{girls} tools into ProM. Despite the weather, it was a great time in Eindhoven!

Many steps toward this thesis were accompanied by coauthors. I really enjoyed the work with you. Thank you Ahmed Awad, Alistair Barros, Jan Bretschneider, C{\'e}dric Favre, Remco Dijkman, Jana Koehler, Dieter K\"onig, Frank Michael Kraft, Marcello La Rosa, Frank Leymann, Nannette Liske, Simon Moser, Chun Ouyang, and Hagen V\"olzer. I learned a lot!

The software tools used in this thesis are the result of solid teamwork. I thank Stephan Mennicke, Dennis Reinert, Georg Straube, Christian Sura, Robert Waltemath, and Martin Znamirowski for their help and timely last-minute support.

In the years of my PhD, there were so many helpful people in the background that made the whole procedure so incredibly smooth that I nearly forgot them. I thank Birgit Heene, Riet van Buul, and Ine van der Ligt.

\vspace{3em}

\noindent Thank you!

\bigskip

\noindent Niels Lohmann\\
Rostock, July 2010
